Trip Summary ITHIM-R

### 2019-10-05 code/producing_trips_rd/trip-summary.Rmd
modify trip summary tables

---
title: "Trip Summary ITHIM-R"
author: "Lambed Tatah, MRC Epidemiology Unit, University of Cambridge, UK"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document:
        theme: null
---

```{r, include = FALSE}
source("J:/Group/lambed/ITHIM-R/code/producing_trips_rd/used_functions.R")

@@

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/buenos_aires/buenos_aires_trip.csv")
quality_check(trip)
trip_summary$buenos_aires <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/sao_paulo/sao_paulo_trip.csv")
quality_check(trip)
trip_summary$sao_paulo <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/belo_horizonte/belo_horizonte_trip.csv")
quality_check(trip)
trip_summary$belo_horizonte <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/santiago/santiago_trip.csv")
quality_check(trip)
trip_summary$santiago_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/bogota/bogota_trip.csv")
quality_check(trip)
trip_summary$bogota_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/accra/accra_trip.csv")
quality_check(trip)
trip_summary$accra_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/delhi/delhi_trip.csv")
quality_check(trip)
trip_summary$delhi_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/bangalore/bangalore_trip.csv")
quality_check(trip)
trip_summary$bangalore_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/mexico/mexico_city_trip.csv")
quality_check(trip)
trip_summary$mexico_city <- value

>>>>

---
title: "Trip Summary ITHIM-R"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, include = FALSE}
source("V:/Group/lambed/ITHIM-R/code/producing_trips_rd/used_functions.R")
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')
```

```{r loadLibraries, echo = F, message = F}

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary

@@

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/buenos_aires/buenos_aires_trip.csv")
quality_check(trip)
trip_summary$buenos_aires <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/sao_paulo/sao_paulo_trip.csv")
quality_check(trip)
trip_summary$sao_paulo <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/belo_horizonte/belo_horizonte_trip.csv")
quality_check(trip)
trip_summary$belo_horizonte <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/santiago/santiago_trip.csv")
quality_check(trip)
trip_summary$santiago_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/bogota/bogota_trip.csv")
quality_check(trip)
trip_summary$bogota_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/accra/accra_trip.csv")
quality_check(trip)
trip_summary$accra_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/delhi/delhi_trip.csv")
quality_check(trip)
trip_summary$delhi_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/bangalore/bangalore_trip.csv")
quality_check(trip)
trip_summary$bangalore_city <- value

trip <- read_csv("V:/Group/lambed/ITHIM-R/data/local/mexico/mexico_city_trip.csv")
quality_check(trip)
trip_summary$mexico_city <- value
